Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-11 journal/content.tex
Yet one reference on "large scale"
Introduction: Relevance of this study

Software organizations are constantly challenged to function more efficiently,
most often due to the fast evolving software marketplace. Agile methods have
been developed to improve efficiency of software development, but are originally
designed for use in projects of limited size. The benefits of agile are pursued
by large organizations

Despite the

-- Who will be interested of this?

@@

A number of studies on large scale use of agile exist. However, the studies
present either single cases, do not provide a research method, or does not
provide insights on the adoption aspect of large scale agile development.

* There is interest in large scale [ref XP13 workshop] \citep{Dingsoyr2013a}

* Freudenberg, S. and Sharp, H., "The Top 10 Burning Research Questions from
    Practitioners," IEEE Software, pp. 8-9, 2010.

This literature review is intended for researchers as a theoretical and proven
foundation for the real problems that organizations face in transformations.
This is also intended to be directly usable by practitioners, to serve as a
base of general advice with strong motivation.
%(although every organization has unique needs)

Dingsoyr:
The nature of software development, being innovative work that is only partially
compatible with programmed coordination, requires a strong emphasis on personal
communication [Kraut, R. E. and Streeter, L. A., "Coordination in software
development," Communications of the ACM, vol. 38, pp. 69-81, 1995]

@@

As a part of our research, we identified further definitions of large scale. All
of these definitions referred to the number of people involved.
In early work on agile \citet{Fowler2000} regards the Crystal methodology being
suitable for up to 50 people, thus setting a boundary beyond which agile methods
would be expected to need special considerations. Also \citet{Williams2003}
present 50 people as a limit which practitioners and researchers has seen as the
largest organization suitable for agile.
\citet{Elshamy2006} considered a development project large if it had a staff
between 50 and 100 people, including all project personnel. Finally, the largest
numbers were presented by \citet{Moore2008} who define large scale in the scope
of their research as 300 people across 3 sites.

>>>>

Software organizations are constantly challenged to function more efficiently.
In the fast evolving software marketplace  . Agile methods have
been developed to improve efficiency of software development, but are originally
designed for use in projects of limited size.

The benefits of agile are pursued by large organizations

Agile methods are more difficult to implement in large organizations \citep{Dyba2008}.

It is an interesting topic, but agile in large scale is still an evolving
research topic.

@@

% A number of studies on large scale use of agile exist. However, the studies
% present either single cases, do not provide a research method, or does not
% provide insights on the adoption aspect of large scale agile development.

This literature review is targeted for both practitioners and researchers. For
practitioners this work provides a reference of cases describing introduction
of agile methods, which can be valuable in planning or reflecting on a agile
adoption process. The systematic review approach can provide practitioners an
objective view on how agile adoptions typically progress.

Applying agile in large scale has been noted as a current research trend. In
2010 \citet{Freudenberg2010} conducted a survey at the XP conference,
highlighting ``agile and large projects'' as the one of the hottest research
topics. The trend was continued in the 2013 XP conference, where a research
trends workshop focused specifically on large scale agile development. The
viewpoint on introduction of agile methods was highlighted in the workshop
\citep{Dingsoyr2013a}.

Research on agile software development is accumulating and maturing, and has
provided ground for performing systematic literature reviews
\citep{Dyba2008,Jalali2012,Senapathi2013,Kaisti2013}. Still, the area of large
scale agile development has not yet been studied through secondary studies. In
the mean time numerous studies discussing agile adoption have been published.
This setting provides an opportunity to aggregate the findings of primary
studies, and thereby fill a gap in research on large scale agile adoption.

% Dingsoyr:
% The nature of software development, being innovative work that is only partially
% compatible with programmed coordination, requires a strong emphasis on personal
% communication [Kraut, R. E. and Streeter, L. A., "Coordination in software
% development," Communications of the ACM, vol. 38, pp. 69-81, 1995]

@@

As a part of our research, we identified further definitions of large scale. All
of these definitions referred to the number of people involved.
In early work on agile \citet{Fowler2000} regards the Crystal methodology being
suitable for up to 50 people, thus setting a boundary beyond which agile methods
would be expected to need special considerations. Also \citet{Williams2003}
present 50 people as a limit which practitioners and researchers has seen as the
largest organization suitable for agile.
\citet{Koehnemann2009} referred to agile projects including up to 50 people as
small. \citet{Elshamy2006} considered a development project large if it had a
staff between 50 and 100 people, including all project personnel. Finally, the
largest numbers were presented by \citet{Moore2008} who define large scale in
the scope of their research as 300 people across 3 sites.
